\documentclass{scrreprt}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{underscore}
\usepackage[ddmmyyyy]{datetime}
\renewcommand{\dateseparator}{--}
\usepackage[bookmarks=true]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{graphicx}

\newenvironment{enum}
{\begin{enumerate}[label*=\arabic*.][resume]}
{\end{enumerate}}

\hypersetup{
    bookmarks=false,    % show bookmarks bar?
    pdftitle={Software Test Case Document},    % title
    pdfauthor={John Zlotek},                     % author
    pdfsubject={TeX and LaTeX},                        % subject of the document
    pdfkeywords={TeX, LaTeX, graphics, images}, % list of keywords
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=blue,       % color of internal links
    citecolor=black,       % color of links to bibliography
    filecolor=black,        % color of file links
    urlcolor=purple,        % color of external links
    linktoc=page            % only page is linked
}%
\def\myversion{1.0.0 }
\date{}
%\title{%

%}
\usepackage{hyperref}
\begin{document}

\begin{flushright}
    \rule{16cm}{5pt}\vskip1cm
    \begin{bfseries}
        \Huge{SOFTWARE TEST CASE\\ DOCUMENT}\\
        \vspace{1.0cm}
        for\\
        \vspace{1.0cm}
        Checkers\\
        \vspace{1.5cm}
        \LARGE{Version \myversion approved}\\
        \vspace{1.5cm}
        Prepared by:\\
    John Zlotek\\
    Matt Horger\\
    Jake Carfagno\\
    Preet Patel\\
        \vspace{1.9cm}
        Team: \textbf{Big Chungus}\\
        \vspace{1cm}
        \today\\
    \end{bfseries}
\end{flushright}

\tableofcontents

\chapter*{Revision History}

\begin{center}
    \begin{tabular}{|c|c|c|c|}
        \hline
        Name & Date & Reason For Changes & Version\\
        \hline
        1.0.0 & \formatdate{11}{7}{29} & Initial Structure & mhorger\\
        \hline
    \end{tabular}
\end{center}

\chapter{Introduction}
	\section{Purpose of Document}
		This section will detail what we are trying to cover with our tests.
	\section{Scope of Document}
		This section will detail the scope (design doc) of which we are testing.
	\section{Overview of Document}	
		This section will be used for definitions, references, any other review information.

\chapter{Testing Environments}
	\section{Windows}
		This section will describe how we are testing our main client on windows. Can detail linux tests here.
	\section{Ubuntu Images}
		This section will describe how we are testing our server on tux.

\chapter{Setup and Prerequisites}
	\section{Generic Information}
	\section{Steps}

\chapter{Test Cases}
	\section{Client}
		\item Description
		\item Pre-conditions
		\item Scenario
	\section{Server}
		\item Description
		\item Pre-conditions
		\item Scenario
	\section{Game}
		\item Description
		\item Pre-conditions
		\item Scenario
	\section{Miscellaneous}
		\item Description
		\item Pre-conditions
		\item Scenario


\begin{thebibliography}{9}

\bibitem{checkersFoundation}
  The American Checker Foundation,
  \textit{USA Checkers},
  https://www.usacheckers.com/,
  2019.

\bibitem{historyCheckers}
W.J. Rayment,
\textit{History of Checkers or Draughts},
http://www.indepthinfo.com/checkers/history.shtml,
2004.

\end{thebibliography}


\end{document}
